# Setup 
In the following code snippet, we install the relevant packages (if not already installed) and load them into our environment.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require('tidyverse')) install.packages("tidyverse") # data wrangling
if (!require('marginaleffects')) install.packages("marginaleffects") # marginaleffects
```

# Import and description of the data
We import our data and get a brief overview into the variables it contains.

```{r}
df <- read.csv("ESS11.csv")
summary(df)
```


# Descriptive statistics
To get an idea of the structure of variables, we can use the table() command for variables.

```{r}
table(df$prtcleat)        # Which party Austrians feel close to...
```

We'll only get numeric values which we can transform to character labels for better visualization (just follow the codebook here). Some labels (here: 66, 77 and 88) denote so-called missing values, i.e., values which are usually not suitable for analysis (such as: not applicable, don't know, coding error, etc.).

We can use dplyr from the tidyverse to clean our variable.
```{r}
df <- df %>%
  mutate(ptv_austria = case_when(prtcleat == 1 ~ "SPÖ",
                              prtcleat == 2 ~ "ÖVP",
                              prtcleat == 3 ~ "FPÖ",
                              prtcleat == 4 ~ "JETZT",
                              prtcleat == 5 ~ "GRÜNE",
                              prtcleat == 6 ~ "KPÖ",
                              prtcleat == 7 ~ "NEOS",
                              prtcleat == 8 ~ "Others"
                              ))
```

Let's try to plot the party vote with ggplot -- the visualization command from the tidyverse.

```{r}
df %>%
  filter(!is.na(ptv_austria)) %>%
  ggplot(aes(ptv_austria)) +
  geom_bar()
```


***Your Turn***
Choose a country and try to repeat the steps to visualize the distribution of the vote choice. 

```{r}

```


# Bivariate statistics

We have only plotted the distribution of one variable so far. However, we are often interested in relations between two or even more variables.

Let's create a correlation matrix between two variables - one is left-right and the other one is the income. Is there a relationship between income and political attitudes?

```{r}
# first, check the variables:
table(df$lrscale)
table(df$hinctnta) # only available in deciles (not optimal, but ok for now)

df <- df %>%
  mutate(lrscale = ifelse(lrscale > 10, NA, lrscale),
         hinctnta = ifelse(hinctnta > 10, NA, hinctnta)) # easy way to change values (all larger than 10 in these cases) to NA 

df %>%
  filter(!is.na(lrscale) & !is.na(hinctnta)) %>% # we can't create a correlation for missing values, so remove them
  summarise(cor(lrscale, hinctnta))
```
This relationship is almost non-existent.



***Your Turn***
Try the same for education (eisced). Be aware of missing values! 

```{r}
table(df$eisced)
```


***Solution***
```{r}
df <- df %>%
  mutate(edu = ifelse(eisced<55, NA, eisced)) 

df %>%
  filter(!is.na(lrscale) & !is.na(edu)) %>% 
  summarise(cor(lrscale, edu)) # strictly speaking, education is not a numeric variable (it's categorical, so other measures like kendall's tau or regression frameworks would be more appropriate)
```



# Regression framework

Let us try to map the influence of the occupation on left-right position (coming closer to the article by Marks et al. 2023).

To create the social classes, there is a bit more manipulation necessary. The following script is based on Oesch's class scheme (https://people.unil.ch/danieloesch/scripts/)
```{r}
df$isco_mainjob <- df$isco08
df$isco_mainjob <- ifelse(df$isco_mainjob %in% c(66666,77777,88888,99999),-9, df$isco_mainjob)

#### Recode employment status for respondents
df$emplrel_r <- df$emplrel
df$emplrel_r <- ifelse(df$emplrel_r %in% c(6,7,8,9),9, df$emplrel_r)


df$emplno_r <- df$emplno
df$emplno_r[is.na(df$emplno_r)] <- 0
df$emplno_r[df$emplno_r >= 1 & df$emplno_r <= 9] <- 1
df$emplno_r[df$emplno_r >= 10 & df$emplno_r <= 66665] <- 2

df$selfem_mainjob <- NA
df$selfem_mainjob[df$emplrel_r == 1 | df$emplrel_r == 9] <- 1
df$selfem_mainjob[df$emplrel_r == 2 & df$emplno_r == 0] <- 2
df$selfem_mainjob[df$emplrel_r == 3] <- 2
df$selfem_mainjob[df$emplrel_r == 2 & df$emplno_r == 1] <- 3
df$selfem_mainjob[df$emplrel_r == 2 & df$emplno_r == 2] <- 4


#################################################
# Create Oesch class schema for respondents
#################################################

df$class16_r <- -9

# Large employers (1)

df$class16_r[df$selfem_mainjob == 4] <- 1

# Self-employed professionals (2)

df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2000 & df$isco_mainjob <= 2162] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2164 & df$isco_mainjob <= 2165] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2200 & df$isco_mainjob <= 2212] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob == 2250] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2261 & df$isco_mainjob <= 2262] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2300 & df$isco_mainjob <= 2330] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2350 & df$isco_mainjob <= 2352] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2359 & df$isco_mainjob <= 2432] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2500 & df$isco_mainjob <= 2619] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob == 2621] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2630 & df$isco_mainjob <= 2634] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2636 & df$isco_mainjob <= 2640] <- 2
df$class16_r[(df$selfem_mainjob == 2 | df$selfem_mainjob == 3) & df$isco_mainjob >= 2642 & df$isco_mainjob <= 2643] <- 2

# Small business owners with employees (3)

df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob >= 1000 & df$isco_mainjob <= 1439] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob == 2163] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob == 2166] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob >= 2220 & df$isco_mainjob <= 2240] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob == 2260] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob >= 2263 & df$isco_mainjob <= 2269] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob >= 2340 & df$isco_mainjob <= 2342] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob >= 2353 & df$isco_mainjob <= 2356] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob >= 2433 & df$isco_mainjob <= 2434] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob == 2620] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob == 2622] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob == 2635] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob == 2641] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob >= 2650 & df$isco_mainjob <= 2659] <- 3
df$class16_r[df$selfem_mainjob == 3 & df$isco_mainjob >= 3000 & df$isco_mainjob <= 9629] <- 3

# Small business owners without employees (4)

df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob >= 1000 & df$isco_mainjob <= 1439] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob == 2163] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob == 2166] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob >= 2220 & df$isco_mainjob <= 2240] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob == 2260] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob >= 2263 & df$isco_mainjob <= 2269] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob >= 2340 & df$isco_mainjob <= 2342] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob >= 2353 & df$isco_mainjob <= 2356] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob >= 2433 & df$isco_mainjob <= 2434] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob == 2620] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob == 2622] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob == 2635] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob == 2641] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob >= 2650 & df$isco_mainjob <= 2659] <- 4
df$class16_r[df$selfem_mainjob == 2 & df$isco_mainjob >= 3000 & df$isco_mainjob <= 9629] <- 4

# Technical experts (5)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2100 &  df$isco_mainjob <= 2162] <- 5
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2164 &  df$isco_mainjob <= 2165] <- 5
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2500 &  df$isco_mainjob <= 2529] <- 5

# Technicians (6)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3100 &  df$isco_mainjob <= 3155] <- 6
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3210 &  df$isco_mainjob <= 3214] <- 6
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3252] <- 6
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3500 &  df$isco_mainjob <= 3522] <- 6

# Skilled manual (7)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 6000 &  df$isco_mainjob <= 7549] <- 7
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 8310 &  df$isco_mainjob <= 8312] <- 7
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 8330] <- 7
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 8332 &  df$isco_mainjob <= 8340] <- 7
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 8342 &  df$isco_mainjob <= 8344] <- 7

# Low-skilled manual (8)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 8000 &  df$isco_mainjob <= 8300] <- 8
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 8320 &  df$isco_mainjob <= 8321] <- 8
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 8341] <- 8
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 8350] <- 8
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 9200 &  df$isco_mainjob <= 9334] <- 8
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 9600 &  df$isco_mainjob <= 9620] <- 8
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 9622 &  df$isco_mainjob <= 9629] <- 8

# Higher-grade managers and administrators (9)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 1000 &  df$isco_mainjob <= 1300] <- 9
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 1320 &  df$isco_mainjob <= 1349] <- 9
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2400 &  df$isco_mainjob <= 2432] <- 9
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2610 &  df$isco_mainjob <= 2619] <- 9
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2631] <- 9
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 100 &  df$isco_mainjob <= 110] <- 9

# Lower-grade managers and administrators (10)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 1310 &  df$isco_mainjob <= 1312] <- 10
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 1400 &  df$isco_mainjob <= 1439] <- 10
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2433 &  df$isco_mainjob <= 2434] <- 10
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3300 &  df$isco_mainjob <= 3339] <- 10
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3343] <- 10
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3350 &  df$isco_mainjob <= 3359] <- 10
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3411] <- 10
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5221] <- 10
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 200 &  df$isco_mainjob <= 210] <- 10

# Skilled clerks (11)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3340 &  df$isco_mainjob <= 3342] <- 11
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3344] <- 11
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 4000 &  df$isco_mainjob <= 4131] <- 11
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 4200 &  df$isco_mainjob <= 4221] <- 11
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 4224 &  df$isco_mainjob <= 4413] <- 11
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 4415 &  df$isco_mainjob <= 4419] <- 11

# Unskilled clerks (12)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 4132] <- 12
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 4222] <- 12
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 4223] <- 12
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5230] <- 12
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 9621] <- 12

# Socio-cultural professionals (13)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2200 &  df$isco_mainjob <= 2212] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2250] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2261 &  df$isco_mainjob <= 2262] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2300 &  df$isco_mainjob <= 2330] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2350 &  df$isco_mainjob <= 2352] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2359] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2600] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2621] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2630] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2632 &  df$isco_mainjob <= 2634] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2636 &  df$isco_mainjob <= 2640] <- 13
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2642 &  df$isco_mainjob <= 2643] <- 13

# Socio-cultural semi-professionals (14)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2163] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2166] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2220 &  df$isco_mainjob <= 2240] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2260] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2263 &  df$isco_mainjob <= 2269] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2340 &  df$isco_mainjob <= 2342] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2353 &  df$isco_mainjob <= 2356] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2620] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2622] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2635] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 2641] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 2650 &  df$isco_mainjob <= 2659] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3200] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3220 &  df$isco_mainjob <= 3230] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3250] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3253 &  df$isco_mainjob <= 3257] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3259] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3400 &  df$isco_mainjob <= 3410] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3412 &  df$isco_mainjob <= 3413] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3430 &  df$isco_mainjob <= 3433] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3435] <- 14
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 4414] <- 14

# Skilled service (15)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3240] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3251] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3258] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 3420 &  df$isco_mainjob <= 3423] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 3434] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5000 &  df$isco_mainjob <= 5120] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5140 &  df$isco_mainjob <= 5142] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5163] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5165] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5200] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5220] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5222 &  df$isco_mainjob <= 5223] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5241 &  df$isco_mainjob <= 5242] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5300 &  df$isco_mainjob <= 5321] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5400 &  df$isco_mainjob <= 5413] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5419] <- 15
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 8331] <- 15

# Low-skilled service (16)

df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5130 &  df$isco_mainjob <= 5132] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5150 &  df$isco_mainjob <= 5162] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5164] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5169] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5210 &  df$isco_mainjob <= 5212] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5240] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5243 &  df$isco_mainjob <= 5249] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 5322 &  df$isco_mainjob <= 5329] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 5414] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob == 8322] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 9100 &  df$isco_mainjob <= 9129] <- 16
df$class16_r[df$selfem_mainjob == 1 & df$isco_mainjob >= 9400 &  df$isco_mainjob <= 9520] <- 16


df$class16_r[df$class16_r == -9] <- NA
df <- df %>%
  mutate(class16_r = case_when(class16_r==1 ~ "Large employers",
                             class16_r==2 ~ "Self-employed professionals",
                             class16_r==3 ~ "Small business owners with employees",
                             class16_r==4 ~ "Small business owners without employees",
                             class16_r==5 ~ "Technical experts",
                             class16_r==6 ~ "Technicians",
                             class16_r==7 ~ "Skilled manual",
                             class16_r==8 ~ "Low-skilled manual",
                             class16_r==9 ~ "Higher-grade managers and administrators",
                             class16_r==10 ~ "Lower-grade managers and administrators",
                             class16_r==11 ~ "Skilled clerks",
                             class16_r==12 ~ "Unskilled clerks",
                             class16_r==13 ~ "Socio-cultural professionals",
                             class16_r==14 ~ "Socio-cultural professionals",
                             class16_r==15 ~ "Skilled service",
                             class16_r==16 ~ "Low-skilled service"))


df$class8_r <- NA
df$class8_r[df$class16_r <= "Self-employed professionals"] <- 1
df$class8_r[df$class16_r == "Small business owners with employees" | df$class16_r == "Small business owners without employees"] <- 2
df$class8_r[df$class16_r == "Technical experts" | df$class16_r == "Technicians"] <- 3
df$class8_r[df$class16_r == "Skilled manual" | df$class16_r == "Low-skilled manual"] <- 4
df$class8_r[df$class16_r == "Higher-grade managers and administrators" | df$class16_r == "Lower-grade managers and administrators"] <- 5
df$class8_r[df$class16_r == "Skilled clerks" | df$class16_r == "Unskilled clerks"] <- 6
df$class8_r[df$class16_r == "Socio-cultural professionals" | df$class16_r == "Socio-cultural professionals"] <- 7
df$class8_r[df$class16_r == "Skilled service" | df$class16_r == "Low-skilled service"] <- 8

df <- df %>%
  mutate(class8_r = case_when(class8_r==1 ~ "Self-employed professionals and large employers",
                            class8_r==2 ~ "Small business owners",
                            class8_r==3 ~ "Technical (semi-)professionals",
                            class8_r==4 ~ "Production workers",
                            class8_r==5 ~ "(Associate) managers",
                            class8_r==6 ~ "Clerks",
                            class8_r==7 ~ "Socio-cultural (semi-)professionals",
                            class8_r==8 ~ "Service workers"))

# we transform the variable to a factor which is easier to handle in regression analyses
df <- df %>%
  mutate(class8_r = as.factor(class8_r),
         class8_r = relevel(class8_r, ref="Production workers")) # let's set production workers as a "reference category" to compare other groups to construction workers
```

Regress!
```{r}
m1 <- lm(lrscale ~ class8_r, df)
summary(m1)


# plot! (here only for some selected groups, we could add more or all)
pred_val <- predictions(m1, newdata = datagrid(class8_r = c("(Associate) managers", "Clerks", "Socio-cultural (semi-)professionals", 
                                                   "Service workers", "Production workers")))
pred_val %>%
  ggplot(aes(class8_r, estimate)) + 
  geom_point() + geom_errorbar(aes(ymin=conf.low, ymax=conf.high))
```

We should be aware that a bivariate regression cannot tell us much about causality. It's possible that the relationship is spurious - class might actually correlate a lot with other items like education, income etc. which might confound our relationship.

***Your Turn***

If you want, add more variables to the regression and see how coefficients change.

```{r}

```


***Solution***

```{r}
df <- df %>%
  mutate(gender = ifelse(gndr==1, "Male", "Female"),
         age = ifelse(agea<999,agea,NA),
         edu_cat = as.factor(case_when(eisced == 1 ~ "Less than lower secondary",
                             eisced == 2 ~ "Lower secondary",
                             eisced == 3 ~ "Lower tier upper secondary",
                             eisced == 4 ~ "Upper tier upper secondary",
                             eisced == 5 ~ "Advanced vocational, sub-degree",
                             eisced == 6 ~ "Lower tertiary",
                             eisced == 7 ~ "Higher tertiary")),
         edu_cat = relevel(edu_cat, ref="Less than lower secondary"))

m2 <- lm(lrscale ~ class8_r + edu_cat + gender + age, df)
summary(m2)
```


# Measuring policy polarization
The European Social Survey does not have appropriate measures regarding affective polarization (at least in Wave 11). However, it allows to conceptualize policy polarization as Bischof and Wagner (2019) did. 

```{r}
df <- df %>%
  mutate(lr_pol = (lrscale - median(lrscale, na.rm=T))^2)

# individual distribution
df %>%
  ggplot(aes(lr_pol)) + 
  geom_density()

# country-level aggregate
df %>%
  group_by(cntry) %>%
  summarise(lr_pol_cntry = mean(lr_pol, na.rm=T)) %>%
  ggplot(aes(reorder(cntry, -lr_pol_cntry), lr_pol_cntry)) +
  geom_col()


# explanations of polarization on an individual level
m3 <- lm(lr_pol ~ class8_r + edu_cat + gender + age, df)
summary(m3)

# let's see what happens if we control for country-specific levels of polarization
m4 <- lm(lr_pol ~ class8_r + edu_cat + gender + age + cntry, df)
summary(m4)
``` 