```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require('tidyverse')) install.packages("tidyverse")                      # data wrangling
if (!require('quanteda')) install.packages("quanteda")                        # preprocessing to dfm
if (!require('quanteda.textstats')) install.packages("quanteda.textstats")    # statistics about text
if (!require('quanteda.textplots')) install.packages("quanteda.textplots")    # plots visualizing texts
if (!require('quanteda.textmodels')) install.packages("quanteda.textmodels")  # text models
if (!require('caret')) install.packages("caret")                              # for advanced machine learning
```


# Step 1: Import and preparation of the corpus
In the first step, we import our data set. In this case, we use a sentiment dataset that has classified tweets into "positive", "neutral" and "negative" (https://huggingface.co/datasets/mteb/tweet_sentiment_extraction).

For now, we'll limit ourselves to a binary classification task. This is usually easier. 

```{r}
data <- readRDS("./session9/sentiment_tweets.RDS")
data <- data %>%
  filter(label_text!="neutral")
```

# Step 2: Conversion to dfm object

In the next step, you have to convert the data back into a dfm object.

```{r}
corp_tweet <- corpus(data$text)
toks_tweet <- tokens(corp_tweet,
                     remove_punct=T,
                     remove_symbols=T)
dfm_tweet <- dfm(toks_tweet, tolower=T)

docvars(dfm_tweet, "text_id") <- data$id
docvars(dfm_tweet, "label") <- data$label
docvars(dfm_tweet, "label_text") <- data$label_text
```


# 3. Training and Test Dataset

Now you have to split your datasets into a training and a test dataset. Ensures that both dfm have the same features.

```{r}
set.seed(135)

train <- dfm_sample(dfm_tweet,0.8*nrow(dfm_tweet))
test <- dfm_subset(dfm_tweet,
  !(docnames(dfm_tweet) %in% docnames(train)))

train <- train %>% dfm_trim(1)
test <- dfm_match(test, featnames(train))
```


# 4. Modeling 

Now you can already estimate a model. Start with a Naïve Bayesian classifier.

```{r}
tweets_nb <- textmodel_nb(train,docvars(train, "label"))
tweets_nb
```

# 5. Validation 

Discuss below how well the model performed. Is it better at predicting positive or negative tweets?

```{r}
pred_tweets <- predict(tweets_nb, newdata=test)

confusionMatrix(pred_tweets, as.factor(docvars(test,"label")))
```

# 6. Out-of-sample prediction

Now create your own small dataset of texts that have not yet been seen by your model. Try to predict the sentiment of these texts. How do you rate the performance?

```{r}
new_examples <- c("I am so happy you are here", "You disappoint me", "leave me alone", "That's not fair", "are u joking")
new_tokens <- tokens(new_examples)
new_dfm <- dfm(new_tokens)

# Align the features with the training DFM
new_dfm <- dfm_match(new_dfm, features = featnames(train))


out_of_sample <- predict(tweets_nb, newdata=new_dfm)
out_of_sample
```

# Improvement of prediction

In the following, you should try to improve your prediction. First of all, use logistic regression to see if it predicts the test dataset better.

```{r}
tweets_lr <- textmodel_lr(train,docvars(train, "label"))
pred_tweets2 <- predict(tweets_lr, newdata=test)

confusionMatrix(as.factor(pred_tweets2), as.factor(docvars(test,"label")))
```


Now remove some features from the dfm and run the analysis again with this dfm. Does this improve prediction? 

```{r}
# to dfm
dfm_tweet2 <- dfm(toks_tweet, tolower = T) %>% dfm_trim(min_termfreq = 10,
                                             termfreq_type = "count",
                                             max_docfreq = 0.5,
                                             docfreq_type = "prop")

docvars(dfm_tweet2, "text_id") <- data$id
docvars(dfm_tweet2, "label") <- data$label
docvars(dfm_tweet2, "label_text") <- data$label_text


# identify ids of empty documents
drop_ids <- dfm_tweet2@docvars$docname_[ntoken(dfm_tweet2)==0] %>% str_extract(., "\\d{1,}") %>% as.numeric()

# remove them from data frame
data2 <- data[!row.names(data) %in% drop_ids, ]

# remove them from dfm
dfm_tweet2 <- dfm_subset(dfm_tweet2, ntoken(dfm_tweet2)>0)
dfm_tweet2

# split into train and testing data
set.seed(135)

train2 <- dfm_sample(dfm_tweet2,0.8*nrow(dfm_tweet2))
test2 <- dfm_subset(dfm_tweet2,
  !(docnames(dfm_tweet2) %in% docnames(train2)))

train2 <- train2 %>% dfm_trim(1)
test2 <- dfm_match(test2, featnames(train2))

# modelling
tweets_nb2 <- textmodel_nb(train2,docvars(train2, "label"))

# evaluation
pred_tweets3 <- predict(tweets_nb2, newdata=test2)
confusionMatrix(pred_tweets3, as.factor(docvars(test2,"label")))
```

No.